SAT Competition 2020\tnoteref{title}

### 2021-06-04 paper/main.tex
added individual amounts for crypto submissions

\begin{table}[t]
\centering\small
\begin{tabular}{llrr}
\bf Family & \bf Author & \bf Submitted & \bf Selected\\
\hline\arrayrulecolor{lightgray}
0/1 Integer Programming & \multirow{4}{*}{Riveros} & 6 & 2 \\
Fermat &  & 8 & 5 \\
Schur Coloring &  & 4 & 2 \\
Sum Subset &  & 5 & 2 \\
\hline
Anti-Bandwidth & Biere & 187 & 14 \\
Baseball Lineup & Hickey & 40 & 13 \\
Bit-Vector & Preiner & 393 & 14 \\
Cellular Automata & Chowdhury & 20 & 12 \\
CNF Miter & Manthey & 38 & 7 \\
Coloring & Oostema & 14 & 14 \\
Core-based Generator & Hartung & 20 & 14 \\
Cover & Gacek & 18 & 13 \\
\hline
\multirow{3}{*}{Cryptography} & Paxian & \multirow{3}{*}{106} & \multirow{3}{*}{34} \\
 & Shaw &  &  \\
 & Soos &  &  \\
\hline
Discrete Logarithm & Jingchao & 20 & 7 \\
Edge Matching & Holten & 58 & 7 \\
Flood-It Puzzle & Stiphout & 40 & 0 \\
HGen & Guanfeng & 20 & 13 \\
Hypertree Decomposition & Schidler & 56 & 14 \\
Influence Maximization & Kochemazov & 20 & 14 \\
Lam Discrete Geometry & Nejati & 20 & 9 \\
Polynomial Multiplication & Maoluo & 20 & 8 \\
Station Repacking & Newman & 20 & 12 \\
Stedman Triples & Johnson & 23 & 7 \\
Tensors & Savicky & 20 & 14 \\
Termination Analysis & Yolcu & 12 & 7 \\
Timetable & Djamegni & 20 & 14 \\
Tournament & Heule & 16 & 14 \\
Vlsat & Bouvier & 36 & 14 \\
\arrayrulecolor{black}
\hline
\multicolumn{2}{r}{$\Sigma$} & 1260 & 300
\end{tabular}
\caption{Families and amounts of newly submitted instances}
\label{tab:families}
\end{table}

@@

Backbone variables are defined to be those variables which have the same value in all models of a given instance~\cite{Janota:2015:Backbones}. 
The application \textsf{genipabones} incrementally determines backbone variables in a given satisfiable SAT instances using the dual rail encoding~\cite{Balyo:2015:SATRace}.
We selected $50$ of the smallest and easiest satisfiable instances from previous SAT competitions to evaluate solver performance with this application.

>>>>

\newcommand{\curly}[1]{\multirow{3}{*}{$\hspace{-1em}\left\rbrace\begin{array}{r}~\\#1\\~\end{array}\right.$}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}
\begin{table}[t]
\centering\small
\begin{tabularx}{.94\linewidth}{llRrRr}
\bf Family & \bf Author & \multicolumn{2}{l}{\bf Submitted} & \multicolumn{2}{l}{\bf Selected}\\
\hline\arrayrulecolor{lightgray}
0/1 Integer Programming & \multirow{4}{*}{Riveros} & 6 & & 2 & \\
Fermat &  & 8 & & 5 & \\
Schur Coloring &  & 4 & & 2 & \\
Sum Subset &  & 5 & & 2 & \\
\hline
Anti-Bandwidth & Biere & 187 & & 14 & \\
Baseball Lineup & Hickey & 40 & & 13 & \\
Bit-Vector & Preiner & 393 & & 14 & \\
Cellular Automata & Chowdhury & 20 & & 12 & \\
CNF Miter & Manthey & 38 & & 7 & \\
Coloring & Oostema & 14 & & 14 & \\
Core-based Generator & Hartung & 20 & & 14 & \\
Cover & Gacek & 18 & & 13 & \\
%\hline
\multirow{3}{*}{Cryptography} & Paxian & 50 & \arraycolsep=1pt\curly{106} & 6 & \arraycolsep=1pt\curly{34} \\
 & Shaw & 20 & & 14 & \\
 & Soos & 36 & & 14 & \\
%\hline
Discrete Logarithm & Jingchao & 20 & & 7 & \\
Edge Matching & Holten & 58 & & 7 & \\
Flood-It Puzzle & Stiphout & 40 & & 0 & \\
HGen & Guanfeng & 20 & & 13 & \\
Hypertree Decomposition & Schidler & 56 & & 14 & \\
Influence Maximization & Kochemazov & 20 & & 14 & \\
Lam Discrete Geometry & Nejati & 20 & & 9 & \\
Polynomial Multiplication & Maoluo & 20 & & 8 & \\
Station Repacking & Newman & 20 & & 12 & \\
Stedman Triples & Johnson & 23 & & 7 & \\
Tensors & Savicky & 20 & & 14 & \\
Termination Analysis & Yolcu & 12 & & 7 & \\
Timetable & Djamegni & 20 & & 14 & \\
Tournament & Heule & 16 & & 14 & \\
Vlsat & Bouvier & 36 & & 14 & \\
\arrayrulecolor{black}
\hline
\multicolumn{2}{r}{$\Sigma$} & 1260 & & 300 & 
\end{tabularx}
\caption{Families and amounts of newly submitted instances}
\label{tab:families}
\end{table}

@@

Backbone variables are defined to be those variables which have the same value in all models of a given instance~\cite{Monasson:1999,Janota:2015:Backbones}. 
The application \textsf{genipabones} incrementally determines backbone variables in a given satisfiable SAT instances using the dual rail encoding~\cite{Balyo:2015:SATRace}.
We selected $50$ of the smallest and easiest satisfiable instances from previous SAT competitions to evaluate solver performance with this application.
